RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
note the possibility of using the user name (env var $USER) as an annotation

`RNeXML` automatically adds basic metadata by default such as a timestamp
of when the tree was produced and an open data license (CC0, compatible
with deposition on Dryad data repository), which can be configured
as needed.

>>>>

<!-- in the Perl library I also embed the value of the environment variable
$USER as a document-level annotation -->
`RNeXML` automatically adds basic metadata by default such as a timestamp
of when the tree was produced and an open data license (CC0, compatible
with deposition on Dryad data repository), which can be configured
as needed.
